
## Loading and preprocessing the data

load data 
```{r}
rawdata <- read.csv("activity.csv")
```
preprocessing (removing NA for first analysis)...  
```{r}
cleaned <- rawdata[complete.cases(rawdata),]
stepsPerDay <- sapply(split(cleaned$steps, cleaned$date),sum)
```

## What is mean total number of steps taken per day?

Make a histogram of the total number of steps taken each day  
```{r}
hist(stepsPerDay, col="red", main="Steps per day",ylim=c(0,40))
```

Calculate and report the mean and median total number of steps taken per day:  
this is the mean  
```{r}
print(mean(stepsPerDay))
```
this is the median  
```{r}
print(median(stepsPerDay))
```

## What is the average daily activity pattern?

```{r}
stepsPerInt <-sapply(split(cleaned$steps, cleaned$interval), mean)
plot(stepsPerInt, type = "l", , xlab = "Interval", ylab = "Number of steps")
```
Max in daily number of steps  
```{r}
  names(stepsPerInt[stepsPerInt==max(stepsPerInt)])
```
## Imputing missing values

the number of missing values in the initial dataset  
```{r}
sum(is.na(rawdata$steps))
```
fill the data for missing values with the average of each interval...  
```{r}
filled=rawdata
for (i in 1:nrow(filled)) {
    if (is.na(filled[i, "steps"])) {
        interval = as.character(filled[i, "interval"])
        filled[i, "steps"] = stepsPerInt[interval]
    }
}
```
Make a histogram of the total number of steps taken each day  
```{r}
stepsPerDayF <- sapply(split(cleaned$steps, cleaned$date),sum)
hist(stepsPerDayF, col="blue", main="Steps per Day \n (with NA replaced by calculated data)",ylim=c(0,40))
```
Calculate and report the mean and median total number of steps taken per day:  
this is the mean  
```{r}
print(mean(stepsPerDayF))
```
this is the median  
```{r}
print(median(stepsPerDayF))
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
```
